Supplemental Material for submission ``Do Objects in Real-World Images Have a Canonical Name?''

### 2019-05-16 papers/EMNLP2019/analysis2.tex
starts to add some results in modeling

\begin{table}
\small
\begin{tabular}{lcc|cc}
\toprule
 & \multicolumn{2}{c}{all MN variants} &  \multicolumn{2}{c}{MN $n > 10$} \\
        relation & \%token &    \%types & \%token &    \%types \\
\midrule
\multicolumn{2}{c}{\it easy to recover}\\
 meronymy &  0.3 &  0.9 &  0.8 &  1.0 \\
 synonymy &  1.8 &  6.4 &  2.5 &  7.2 \\
 hypernymy &  8.8 &  28.2 &  11.0 &  31.3 \\
\midrule
\multicolumn{2}{c}{\it difficult to recover}\\
holonymy.1 &  0.2 &  0.8 &  0.3 &  0.9 \\
 co-hyponymy &  4.8 &  6.2 &  6.0 &  6.4 \\
 hyponymy &  4.9 &  6.6 &  5.5 &  6.9 \\
 \midrule
 \multicolumn{2}{c}{\it not recoverable}\\
 name not covered &  7.8 &  2.8 &  5.8 &  2.1 \\
 rel not covered &  71.3 &  48.1 &  68.0 &  44.2 \\
\bottomrule

\end{tabular}
%\begin{tabular}{lll}
%\toprule
%       relation &  types & tokens \\
%\midrule
%synonymy &  0.01 &  0.09 \\
%co-hyponymy &  0.03 &  0.07 \\
%hypernymy &  0.06 &  0.35 \\
%not-covered &  0.19 &  0.04 \\
%crossclassified &  0.70 &  0.47 \\
%\bottomrule
%\end{tabular}
% \small
% \begin{tabular}{llll}
% \toprule
%         relation & \% types & \% tokens & av. depth \\
% \midrule
%  co-hyponymy (closure, max depth=10) &  0.889 &  0.551 &       3.479 \\
%     hyponymy (closure, max depth=10) &  0.097 &  0.328 &       2.204 \\
%         synonymy &  0.015 &  0.121 &       1.000 \\
% \bottomrule
% \end{tabular}

@@

>>>>

\begin{table}
\small
\centering
\begin{tabular}{lcc}
\toprule
         relation & \% types & \% token \\
\midrule
 meronym &  0.1 &  0.2 \\
 holonym &  0.1 &  0.4 \\
 synonym &  1.1 &  1.1 \\
 hyponym &  2.2 &  3.8 \\
 co-hyponym &  3.1 &  5.9 \\
 hypernym &  10.5 &  27.7 \\
 word-not-covered &  10.6 &  2.6 \\
 rel-not-covered &  72.2 &  58.3 \\
\bottomrule
\end{tabular}

%\begin{tabular}{lll}
%\toprule
%       relation &  types & tokens \\
%\midrule
%synonymy &  0.01 &  0.09 \\
%co-hyponymy &  0.03 &  0.07 \\
%hypernymy &  0.06 &  0.35 \\
%not-covered &  0.19 &  0.04 \\
%crossclassified &  0.70 &  0.47 \\
%\bottomrule
%\end{tabular}
% \small
% \begin{tabular}{llll}
% \toprule
%         relation & \% types & \% tokens & av. depth \\
% \midrule
%  co-hyponymy (closure, max depth=10) &  0.889 &  0.551 &       3.479 \\
%     hyponymy (closure, max depth=10) &  0.097 &  0.328 &       2.204 \\
%         synonymy &  0.015 &  0.121 &       1.000 \\
% \bottomrule
% \end{tabular}

@@

\begin{figure*}
\begin{minipage}[b]{0.5\linewidth}
{\footnotesize
\setlength{\tabcolsep}{1pt}
\begin{tabular}{cp{4cm}p{4cm}p{4cm}}
\textbf{desk} &  \raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2320949_1048853_singleton_obj.png}} MN: keyboard  &
\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2343219_926143_supercat_unique.png}}  MN: desktop &
\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2354847_1742687_seed_ambiguous.png}} MN: computer \\
\textbf{bench} &  \raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2350360_1042111_supercat_unique.png}} MN: table  &
\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2389358_1261752_singleton_obj.png}}  MN: seat &
\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/1593011_2063521_singleton_obj.png}} MN: wood \\
\textbf{sandwich} &  \raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2352086_856151_supercat_unique.png}} MN: burger  &
\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2352833_1884120_supercat_unique.png}}  MN: plate &
\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2343230_2309969_supercat_unique.png}} MN: bun\\ 
\textbf{girl} &  \raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2400735_406112_singleton_obj.png}} MN: t-shirt  &
\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2329628_3363001_singleton_obj.png}}  MN: tennis player &
\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2315383_1055824_singleton_obj.png}} MN: kid\\ 
\textbf{truck} &  \raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2317240_1022463_singleton_obj.png}} MN: wheel  &
\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2410889_361670_singleton_obj.png}}  MN: bus &
\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2334129_965945_singleton_obj.png}} MN: trailer\\ 
\textbf{bridge} &  \raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2349701_3192266_supercat_unique.png}} MN: train  &
\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2322428_2930306_supercat_unique.png}}  MN: road &
\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2348679_2628081_supercat_unique.png}} MN: dock\\ 
\textbf{bed} &  \raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2400919_1153609_singleton_obj.png}} MN: pillow  &
\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2383991_529114_singleton_obj.png}}  MN: blanket &
\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2343909_918810_singleton_obj.png}} MN: table\\

\end{tabular}

}
\end{minipage}

 \caption{\label{fig:ex}Examples from MN data set, where no relation between VG synset (in bold) and name annotation can be found}
\end{figure*}
